The ChEMBL database as Linked Open Data

### 2012-07-17 article.tex
Some fixes in the Refs section; still need a proper biblatex style for BioMed Central

\usepackage{a4wide}  % Formatting web addresses  
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp,sorting=none]{biblatex}
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{article.bib}

@@

The current scientific data deluge, in which datasets grow faster in size and complexity than scientists can handle,
provides several new challenges for information systems. Scientists wish to 
discover new, unique, and significant patterns in datasets, which explaining biological 
phenomena not yet understood. This process requires integration of datasets that are both 
sparse, and growing independent of one another. The discovery of new patterns showing the 
causes and effects of various biological phenomena is beyond the scope of single datasets.
For example, systems biologists integrate micro-array differential expression datasets to 
biological pathways, using various other datasets to provide evidence for the links~\cite{Staab2007}. 
Another prominent example is drug discovery where a new unique chemical entity is discovered 
based on descriptions of its biological properties. This process requires the effective 
linkage of many scientific datasets~\cite{Samwald2011,OpenPHACTS}.

>>>>

\usepackage{a4wide}  % Formatting web addresses  
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp,sorting=none,firstinits=true,doi=false,isbn=false,url=false]{biblatex}
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{article.bib}

@@

The current scientific data deluge, in which datasets grow faster in size and complexity than scientists can handle,
provides several new challenges for information systems. Scientists wish to 
discover new, unique, and significant patterns in datasets, which explaining biological 
phenomena not yet understood. This process requires integration of datasets that are both 
sparse, and growing independent of one another. The discovery of new patterns showing the 
causes and effects of various biological phenomena is beyond the scope of single datasets.
For example, systems biologists integrate micro-array differential expression datasets to 
biological pathways, using various other datasets to provide evidence for the links~\cite{Staab2007}. 
Another prominent example is drug discovery where a new unique chemical entity is discovered 
based on descriptions of its biological properties. This process requires the effective 
linkage of many scientific datasets~\cite{Samwald2011,Williams2012}.
